Classless Java: Tuning Java Interfaces

### 2015-12-03 paper/sections/FutureWork.tex
revise future work

Methods originally defined in Java class \Q@Object@, as \Q@clone@ and
\Q@toString@, can be supported by our approach, but they need special
care. If an interface annotated with \mixin asks an implementation for
\Q@clone@, \Q@toString@, \Q@equals@ or \Q@hashCode@ we can easily
generate one from the fields.\footnote{In particular, for clone we can
  do automatic return type refinement as we do for \Q@with-@ and
  fluent setters. Note how this would solve most of the Java ugliness
  related to \Q@clone@ methods.}
However, if the user wishes to provide his own implementation, since the method is
also implemented in \Q@Object@, a conflict arises. The generated code can resolve the conflict inside \Q@of@, by implementing the method and
delegating it to the user implementation, thus
\begin{lstlisting}
@Obj interface Point{ int x(); int y();
  default Point clone(){ return Point.of(0,0);}//user defined clone
}
\end{lstlisting} 
Would expand into

\begin{lstlisting}
interface Point{ int x(); int y();
  default Point clone(){ return Point.of(0,0);}//user defined clone
  public static Point of(int _x, int _y){
    return new Point(){...
      public Point clone(){ return Point.super.clone();}
    };}}
\end{lstlisting}

>>>>

Methods originally defined in Java class \Q@Object@, as \Q@clone@ and
\Q@toString@, can be supported by our approach with special care. If an
interface annotated with \mixin asks an implementation for \Q@clone@,
\Q@toString@, \Q@equals@ or \Q@hashCode@ we can easily generate one from the
fields.\footnote{In particular, for clone we can do automatic return type
  refinement as we do for \Q@with-@ and fluent setters. Note how this would
  solve most of the Java ugliness related to \Q@clone@ methods.}  However, if
the user wishes to provide his own implementation, since the method is also
implemented in \Q@Object@, a conflict arises. The generated code can resolve the
conflict inside \Q@of@, by implementing the method and delegating it to the user
implementation, thus

\begin{lstlisting}
@Obj interface Point{ int x(); int y();
  default Point clone(){ return Point.of(0,0);}}//user defined clone
\end{lstlisting} 
would expand into

\begin{lstlisting}
interface Point{ ...
  public static Point of(int _x, int _y){
    return new Point(){...
      public Point clone(){ return Point.super.clone();}};}}
\end{lstlisting}
